Something about lineage metrics

### 2018-03-28 paper.tex
Update on Overleaf.

For the most part, the metrics we propose here will center around the evolutionary history of lineages in the population.

% @AML: Currently taking a crack at this bit of the intro (introducing lineages, etc) on paper at the moment!

@@

\section{Results and Discussion}
% Changing mutation: here's what happens when we change mutation on each problem
% - Metric 1
% Problem 1
% Problem 2
% Problem 3
% Problem 4
% - Metric 2
% ...

@@

\section{Text Bank Because I'm not totally sure where things should go}
% Some gibberish on lineages
A lineage describes a chain of ancestors and their descendants where links in the chain are (typically) connected via parent-offspring relationships. In nature, every extant individual has a unique lineage that can be traced back to a single common ancestor. Depending on the modes of replication and variation employed along the lineage (\textit{e.g.} sexual reproduction, horizontal gene transfer), a lineage can be more or less challenging to disentangle. 
% something something something, we focus on asexual populations w/no HGT because easy starting place.

% Some gibberish on how we can represent lineages as sequences of states
Lineages can be imagined as a sequence of states where each state represents an individual. We can characterize each of these states: a phenotype, a genotype, a set of mutations (which may be empty) that differentiate genotype from parent genotype, time of birth/death, etc. 
Given sequences, can apply diagnostic metrics...

% Some gibberish on abstractions over the sequences of states
We can start to make abstractions: state = genotype, state = phenotype, state = location in environment.
Lineage length is measured over these abstractions:
%- Length in number of individuals 
%- Length in number of genotypes
%- Length in number of phenotypes

>>>>

%For the most part, the metrics we propose here will center around the evolutionary history of lineages in the population.

% @AML: Currently taking a crack at this bit of the intro (introducing lineages, etc) on paper at the moment! 
A lineage describes a continuous line of descent, linking ancestors and their descendants. A complete lineage can provide a post-hoc, step-by-step guide to the evolution of an extant organism where each step involves replication and inherited variation. Indeed, lineage analyses are a powerful tool for disentangling the evolution of complexity in both natural and digital systems; digital systems, however, allow for

@@

\section{Results and Discussion}
% Changing mutation: here's what happens when we change mutation on each problem
\begin{figure}
\includegraphics[width=3.5in]{figs/dom_deleterious_mutation_rate.png}
\end{figure}

% - Metric 1
% Problem 1
% Problem 2
% Problem 3
% Problem 4
% - Metric 2
% ...

@@

% \section{Text Bank Because I'm not totally sure where things should go}
% % Some gibberish on lineages
% A lineage describes a chain of ancestors and their descendants where links in the chain are (typically) connected via parent-offspring relationships. In nature, every extant individual has a unique lineage that can be traced back to a single common ancestor. Depending on the modes of replication and variation employed along the lineage (\textit{e.g.} sexual reproduction, horizontal gene transfer), a lineage can be more or less challenging to disentangle. 
% % something something something, we focus on asexual populations w/no HGT because easy starting place.

% % Some gibberish on how we can represent lineages as sequences of states
% Lineages can be imagined as a sequence of states where each state represents an individual. We can characterize each of these states: a phenotype, a genotype, a set of mutations (which may be empty) that differentiate genotype from parent genotype, time of birth/death, etc. 
% Given sequences, can apply diagnostic metrics...

% % Some gibberish on abstractions over the sequences of states
% We can start to make abstractions: state = genotype, state = phenotype, state = location in environment.
% Lineage length is measured over these abstractions:
% %- Length in number of individuals 
% %- Length in number of genotypes
% %- Length in number of phenotypes
